### 2021-06-05 README.Rmd
added JOSS acceptance badge, and fixed link typo

<!-- badges: start -->
[![](https://badges.ropensci.org/428_status.svg)](https://github.com/ropensci/software-review/issues/428)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/ropensci/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/dataaimsr/actions)
[![Codecov test coverage](https://codecov.io/gh/ropensci/dataaimsr/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/dataaimsr?branch=master)
![pkgdown](https://github.com/ropensci/dataaimsr/workflows/pkgdown/badge.svg)
[![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
[![Ask Us Anything
\!](https://img.shields.io/badge/Ask%20us-anything-1abc9c.svg)](https://github.com/ropensci/dataaimsr/issues/new)
![Open Source
Love](https://badges.frapsoft.com/os/v2/open-source.svg?v=103)
<!-- badges: end -->

@@

The Australian Institute of Marine Science (AIMS) has a long tradition in
measuring and monitoring a series of environmental parameters along the
tropical coast of Australia. These parameters include long-term record of sea
surface temperature, wind characteristics, atmospheric temperature, pressure,
chlorophyll-a data, among many others. The AIMS Data Centre team has recently
developed the [AIMS Data Platform API][1] which is a *REST API* providing
JSON-formatted data to users. `dataaimsr` is an **R package** written to
allow users to communicate with the AIMS Data Platform API using an API key
and a few convenience functions to interrogate and understand the datasets
that are available to download. In doing so, it allows the user to
fully explore these datasets in R in whichever capacity they want (e.g.
data visualisation, statistical analyses, etc). The package itself contains
a `plot` method which allows the user to plot summaries of the different types
of dataset made available by the API. Below we provide a brief context about
the existing [Datasets][#datasets] that can be explored through `dataaimsr`.

>>>>

<!-- badges: start -->
[![](https://badges.ropensci.org/428_status.svg)](https://github.com/ropensci/software-review/issues/428)
[![DOI](https://joss.theoj.org/papers/10.21105/joss.03282/status.svg)](https://doi.org/10.21105/joss.03282)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/ropensci/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/dataaimsr/actions)
[![Codecov test coverage](https://codecov.io/gh/ropensci/dataaimsr/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/dataaimsr?branch=master)
![pkgdown](https://github.com/ropensci/dataaimsr/workflows/pkgdown/badge.svg)
[![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
[![Ask Us Anything
\!](https://img.shields.io/badge/Ask%20us-anything-1abc9c.svg)](https://github.com/ropensci/dataaimsr/issues/new)
![Open Source
Love](https://badges.frapsoft.com/os/v2/open-source.svg?v=103)
<!-- badges: end -->

@@

The Australian Institute of Marine Science (AIMS) has a long tradition in
measuring and monitoring a series of environmental parameters along the
tropical coast of Australia. These parameters include long-term record of sea
surface temperature, wind characteristics, atmospheric temperature, pressure,
chlorophyll-a data, among many others. The AIMS Data Centre team has recently
developed the [AIMS Data Platform API][1] which is a *REST API* providing
JSON-formatted data to users. `dataaimsr` is an **R package** written to
allow users to communicate with the AIMS Data Platform API using an API key
and a few convenience functions to interrogate and understand the datasets
that are available to download. In doing so, it allows the user to
fully explore these datasets in R in whichever capacity they want (e.g.
data visualisation, statistical analyses, etc). The package itself contains
a `plot` method which allows the user to plot summaries of the different types
of dataset made available by the API. Below we provide a brief context about
the existing [Datasets](#datasets) that can be explored through `dataaimsr`.
